3.9: Logarithmic Regression - R Practice

### 2019-12-03 content/r/21-r-practice.Rmd
Fix link to r practice 21 answers

Answers:
- [<i class="fas fa-external-link-square-alt"></i> `Answer Key (html)`](/r/19-r-practice-answers.html)
- [<i class="fab fa-markdown"></i> `Answer Key (markdown)`](/r/19-r-practice-answers.Rmd)

>>>>

Answers:

- [<i class="fas fa-external-link-square-alt"></i> `Answer Key (html)`](/r/21-r-practice-answers.html)
- [<i class="fab fa-markdown"></i> `Answer Key (markdown)`](/r/21-r-practice-answers.Rmd)
